\documentclass[a4paper,14pt]{extarticle}
\usepackage{amsmath}
\usepackage[english,ukrainian]{babel}
\usepackage{nameref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[a4paper, left=30mm, right=30mm, top=20mm, bottom=20mm]{geometry}

\title{Dissertation}
\author{}
\date{}

\numberwithin{equation}{section}
\counterwithin{figure}{section}
\linespread{1.5}

\begin{document}

\section*{\centering АНОТАЦІЯ}
\input{anotation}

\section*{\centering ABSTRACT}
\input{abstract}

\section*{\centering СПИСОК ОПУБЛІКОВАНИХ ПРАЦЬ ЗА ТЕМОЮ ДИСЕРТАЦІЇ}
\input{pub_list}

\newpage

\renewcommand{\contentsname}{\centering Зміст}
\tableofcontents

\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Перелік умовних позначень}
\section*{\centering Перелік умовних позначень}
$G$ - модуль зсуву \newline
$E$ - модуль Юнга \newline
$\mu$ - коєфіцієнт Пуасона \newline
$c_1$, $c_2$ - швидкості хвилі \newline
$\omega$ - частота \newline
$\mu_0 = \frac{1}{1 - 2\mu}$ \newline
$\lambda = \frac{\mu E}{(1 + \mu) (1 - 2\mu)}$ - коєфіцієнт Ламе \newline
$U_x(x,y) = u(x,y)$ - переміщення по осі $x$ \newline
$U_y(x,y) = v(x,y)$ - переміщення по осі $y$
\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Вступ}
\section*{\centering Вступ}
\input{introduction}
\newpage

\section[Огляд літератури]{\centering Огляд літератури}
\input{lit_review}
\newpage

\section{МЕТОДИКА ПОБУДОВИ РОЗВ’ЯЗКІВ МІШАНИХ ЗАДАЧ ТЕОРІЇ ПРУЖНОСТІ ДЛЯ ПРЯМОКУТНОЇ ОБЛАСТІ}
\input{general}
\newpage

\section[МІШАНА ЗАДАЧА ТЕОРІЇ ПРУЖНОСТІ ДЛЯ ПРЯМОКУТНОЇ ОБЛАСТІ ЗА УМОВ ІДЕАЛЬНОГО КОНТАКТУ НА БІЧНИХ ГРАНЯХ]
{\centering МІШАНА ЗАДАЧА ТЕОРІЇ ПРУЖНОСТІ ДЛЯ ПРЯМОКУТНОЇ ОБЛАСТІ ЗА УМОВ ІДЕАЛЬНОГО КОНТАКТУ НА БІЧНИХ ГРАНЯХ}
\input{problem_1_intro}
\subsection{Статична задача теорії пружності для прямокутної області за умов ідеального контакту на бічних гранях}
\input{problem_static_1}
\subsection{Динамічна задача теорії пружності для прямокутної області за умов ідеального контакту на бічних гранях}
\input{problem_dynamic_1}

\input{problem_1_summary}
\newpage

\section[МІШАНА ЗАДАЧА ДЛЯ ПРЯМОКУТНОЇ ОБЛАСТІ ЗА УМОВ ДРУГОЇ ОСНОВНОЇ ЗАДАЧІ ТЕОРІЇ ПРУЖНОСТІ НА БІЧНИХ ГРАНЯХ]
{\centering МІШАНА ЗАДАЧА ДЛЯ ПРЯМОКУТНОЇ ОБЛАСТІ ЗА УМОВ ДРУГОЇ ОСНОВНОЇ ЗАДАЧІ ТЕОРІЇ ПРУЖНОСТІ НА БІЧНИХ ГРАНЯХ}
\input{problem_2_intro}
\subsection{Статична задача для прямокутної області за умов другої основної задачі теорії пружності на бічних гранях}
\input{problem_static_2}
\subsection{Динамічна задача для прямокутної області за умов другої основної задачі теорії пружності на бічних гранях}
\input{problem_dynamic_2}

\input{problem_2_summary}
\newpage

\section[ЧИСЛОВІ РОЗРАХУНКИ ТА ЇХ АНАЛІЗ]
{\centering ЧИСЛОВІ РОЗРАХУНКИ ТА ЇХ АНАЛІЗ}
\input{results_discussion.tex}
\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Висновки}
\section*{\centering Висновки}
\input{summary}
\newpage

\begin{thebibliography}{1}
    \bibitem{novacki_1}
    Nowacki W.: Teoria Sprezystosci. Panstwowe Wydawnictwo Naukowe, Warszawa (1970).
    \bibitem{vihak_1}
    V. M. Vihak, M. Y. Yuzvyak, A V. Yasinskij (1998) THE SOLUTION OF THE PLANE THERMOELASTICITY PROBLEM FOR A RECTANGULAR DOMAIN, Journal of Thermal Stresses, 21:5, 545-561, DOI: 10.1080/01495739808956162
    \bibitem{vihak_2}
    Vihak V. M., Tokovyy Yu. (2002) Construction elementary solutions of the elasticity plane problem for the rectangular domain. International applied mechanics. Volume 32, Issue 7, pp. 79-87.
    \bibitem{meleshko_1}
    Grinchenko, V.T. and Meleshko, V.V.: Harmonic Vibrations and Waves in Elastic Bodies [in Russian]. Naukova Dumka, Kiev (1981).
    \bibitem{kushnir_1}
    Kushnir, R.M., Yasinskyy, A.V., Tokovyy, Y.V. Reconstruction of the Thermal Load of a Functionally Graded Hollow Sphere by Surface Displacements. J Math Sci 270, 176–190 (2023). https://doi.org/10.1007/s10958-023-06339-8
    \bibitem{kreyn_1}
    Крейн М. Г. Интегральные уравнения на полупрямой с ядром, зависящим от разности аргументов // УМН. 1958. Т. 13, № 5. С. 3-120.
    \bibitem{zhuravleva_1}
    Zhuravlova Z. Yu. New approach of analytical inversion of Laplace transform for some cases. Researches in Mathematics and Mechanics 24, 122-135 (2019).
    \bibitem{popov_v_1}
    Popov, V.G., Lytvyn, O.V. Stress State of an Elastic Body with Rigid Inclusion in the Form of a Broken Line Under Harmonic Wave Loads. J Math Sci 263, 39–51 (2022). https://doi.org/10.1007/s10958-022-05905-w
    \bibitem{filshtin_1}
    L.A. Fil’shtinskii, Yu.V. Shramko, G.F. Burnatnaya: Model of the Elastic Plate Stiffened with the Regular System of Nanorods. J. Nano- Electron. Phys. 5 No 3, 03020 (2013) http://essuir.sumdu.edu.ua/handle/123456789/31952
    \bibitem{popov_1}
    Popov G., (1982) The elastic stress concentration around dies, cuts, thin, inclusions and reinforcements (in Russian), Nauka, Moscow.
    \bibitem{loboda_1}
    Loboda V. V., Sheveleva A. E. Steady thermal contact of a half strip and a strip // Inzhenerno-Fizicheskii Zhurnal. 1987. Vol. 53, No 2. P. 302-307.


    \bibitem{oden_1}
    Oden J. T., Kikuchi N. (1982) Finite element methods for constrained problems in elasticity. International journal for Numerical Methods in Engineering. Volume 18, Issue 5.
    \bibitem{babushka_1}
    Babuška, I. The finite element method with Lagrangian multipliers. Numer. Math. 20, 179–192 (1973). https://doi.org/10.1007/BF01436561
    \bibitem{maurizio_1}
    Maurizio A., A high-continuity finite element model for two-dimensional elastic problems. Computers and Structures, Volume 21, Issue 5 (1985), Pages 987-993, ISSN 0045-7949, https://doi.org/10.1016/0045-7949(85)90211-1.
    \bibitem{liew_1}
    Liew K. M., Yuming Cheng, Kitipornchai S. (2005) Boundary element-free method (BEFM) and application to two dimensional elasticity problems. International journal for Numerical Methods in Engineering. Vulume 65, Issue 8.
    \bibitem{dong_1}
    Dongyang Shi, Minghao Li, (2014) Superconvergence analysis of the stable conforming rectangular mixed nite elements for the linear elasticity problem Journal of Computati- onal Mathematics. Volume 32, Number 2, pp. 205-214.
    \bibitem{golovchan_1}
    Golovchan, V.T. On the solution of plane boundary-value problems of elasticity in a rectangle. Int Appl Mech 42, 84–89 (2006). https://doi.org/10.1007/s10778-006-0061-8
    
    \bibitem{shyam_1}
    Shyam N. Prasad, Sailendra N. Chatterjee (1973) Some mixed boundary value problems of elasticity in a rectangular domain. International journal of Solids and Structures. Volume 9, Issue 10, pp. 1193-1210.
    \bibitem{kovalenko_1}
    Kovalenko, M.D., Menshova, I.V., Kerzhaev, A.P. et al. A boundary value problem in the theory of elasticity for a rectangle: exact solutions. Z. Angew. Math. Phys. 71, 199 (2020). https://doi.org/10.1007/s00033-020-01425-2
    \bibitem{bantsuri_1}
    Bantsuri, R., Mzhavanadze, Sh. (2007). The mixed problem of the theory of elasticity for a rectangle weakened by unknown equiv-string holes. Proceedings of A. Razmadze Mathematical Institute. 145. 
    \bibitem{kashtalyan_1}
    M Kashtalyan, Three-dimensional elasticity solution for bending of functionally graded rectangular plates, European Journal of Mechanics - A/Solids, Volume 23, Issue 5, 2004, Pages 853-864, ISSN 0997-7538, https://doi.org/10.1016/j.euromechsol.2004.04.002.
    \bibitem{zhuk_1}
    Zhuk, Y.O., Ostos, O.K., Karnaukhova, T.V. Forced Vibrations and Nonstationary Heating of a Rectangular Viscoelastic Plate with Prestresses. Int Appl Mech 58, 423–435 (2022). https://doi.org/10.1007/s10778-022-01167-w
    \bibitem{maksymuk_1}
    Maksymuk, O.V., Sachuk, Y.V., Yatsyuk, S.M. Plane Contact Problems for an Elastic Foundation with Two Bedding Coefficients. J Math Sci 273, 153–162 (2023). https://doi.org/10.1007/s10958-023-06491-1

    \bibitem{popov_4}
    Попов Г. Я. Концентрация упругих напряжений возле штампов разрезов тонких включений и подкреплений. М.: Наука. Главная редакция физико-математической литературы, 1982. 344 с.
    \bibitem{popov_5}
    Попов Г. Я., Абдыманов С. А., Ефимов В. В. Функции и матрицы Грина одномерных краевых задач. Алматы: Изд. Рацах, 1999. 133 с.

    \bibitem{popov_2}
    Попов Г.Я. Точные решения некоторых краевых задач механики деформируемого твѐрдого тела. Одесса: Астропринт, 2013. 424 с.
    \bibitem{popov_3}
    Popov G. On the method of orthogonal polynomials in contact problems of the theory of elasticity. Journal of Applied Mathematics and Mechanics (1969). Volume 33, Issue 3, pp. 503-517
    \bibitem{gantmaher}
    Gantmakher F. R. (1998) The theory of matrices. AMS Chelsea Publishing, Providence, Rohde Island.
    \bibitem{ortogonal}
    Попов Г. Я., Реут В. В., Моісеєв М. Г., Вайсфельд Н. Д. Рівняння математичної фізики. Метод ортогональних многочленів. Одесса: Астропринт, 2010. 120 с.
    \bibitem{prudnikov}
    Прудников А.П.,Брычков Ю.А., Маричев О.И. Интегралы и ряды специальные функции. В 3 т. Т 1. Элементарные функции. 2-е издание, исправленное. М.: ФИЗМАТЛИТ, 2002. 632 с.
    \bibitem{pozhylenkov_1}
    D. Nerukh, O. Pozhylenkov, N. Vaysfeld (2019) Mixed plain boundary value problem of elasticity for a rectangular domain. 25-th International Conference Engineering Mechanics. 2019, May 13-16, Svratka, Czech Republic. p. 255
    \bibitem{pozhylenkov_2}
    O. V. Pozhylenkov (2019) The stress state of a rectangular elastic domain. Researches in Mathematics and Mechanics, Volume 24, Issue 2(34), pp. 88-96
    \bibitem{pozhylenkov_3}
    Пожиленков О. В. Вайсфельд Н. Д. (2019) Мішана крайова задача теорії пружності для прямокутної області. Математичні проблеми механіки неоднорідних структур, випуск 5, Львів, ст. 30-32
    \bibitem{conf_1}
    D. Nerukh, O. Pozhylenkov, N. Vaysfeld 25-th international conference «Engineering Mechanics 2019» // Czech Republic, Svratka, 2019
    \bibitem{conf_2}
    Пожиленков О. В., Вайсфельд Н. Д. Х Мiжнародна наукова конференцiя «Математичнi проблеми механiки неоднорiдних структур» // Львiв, 2019
    \bibitem{pozhylenkov_4}
    O. Pozhyenkov, N. Vaysfeld (2020) Stress state of a rectangular domain with the mixed boundary conditions. Procedia Structural Integrity, Volume 28, pp. 458-463
    \bibitem{conf_3}
    O. Pozhyenkov, N. Vaysfeld «1st Virtual European Conference on Fracture» // Italy, 2020
    \bibitem{pozhylenkov_5}
    O. Pozhyenkov, N. Vaysfeld (2021) Stress state of an elastic rectangular domain under steady load. Procedia Structural Integrity, Volume 33, pp. 385-390
    \bibitem{conf_4}
    O. Pozhyenkov, N. Vaysfeld «26th International Conference on Fracture and Structural Integrity» // Italy, Turin, 2021
    \bibitem{pozhylenkov_6}
    O. Pozhylenkov, N. Vaysfeld (2022) Dynamic mixed problem of elasticity for a rectangular domain. Recent trends in Wave Mechanics and Vibrations, pp. 211-218
    \bibitem{conf_5}
    O. Pozhyenkov, N. Vaysfeld «10th International Conference on Wave Mechanics and Vibrations» // Portugal, Lisbon, 2022
\end{thebibliography}
\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Додаток B ЗНАХОДЖЕННЯ КОРЕНІВ РІВНЯННЯ $det[M(s)]=0$}
\section*{\centering Додаток B}\label{ap_B}
\section*{\centering ЗНАХОДЖЕННЯ КОРЕНІВ РІВНЯННЯ $det[M(s)]=0$}
\input{apendix_b}
\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Додаток C ЗНАХОДЖЕННЯ ФУНДАМЕНТАЛЬНИХ БАЗИСНИХ МАТРИЦЬ $\Psi_i(y)$, $i=\overline{0,1}$}
\section*{\centering Додаток C}\label{ap_C}
\section*{\centering ЗНАХОДЖЕННЯ ФУНДАМЕНТАЛЬНИХ БАЗИСНИХ МАТРИЦЬ $\Psi_i(y)$, $i=\overline{0,1}$}
\input{apendix_c}
\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Додаток D ЗНАХОДЖЕННЯ ФУНКЦІЇ $v_0(y)$ НЕОДНОРІДНОЇ ЗАДАЧІ}
\section*{\centering Додаток D}\label{ap_D}
\section*{\centering ЗНАХОДЖЕННЯ ФУНКЦІЇ $v_0(y)$ НЕОДНОРІДНОЇ ЗАДАЧІ}
\input{apendix_d}
\newpage

\addcontentsline{toc}{section}{\protect\numberline{}Додаток E ЗНАХОДЖЕННЯ КОЄФІЦІЄНТІВ $c_i$, $i=\overline{1,4}$}
\section*{\centering Додаток E}\label{ap_E}
\section*{\centering ЗНАХОДЖЕННЯ КОЄФІЦІЄНТІВ $c_i$, $i=\overline{1,4}$}
\input{apendix_e}
\newpage

\end{document}